MLExplain

### 2018-05-28 paper.tex
Ajoute un bout à la conclusion

\section{Conclusion}
We have shown how JSExplain can be easily adapted to other programming language,
in this case OCaml. Most of the complexity of OCaml being its typing, writing
the interpreter was quite straightforward. As future work, we plan to extend the
subset of OCaml supported by our compiler, to be able to directly use the
standard library when writing interpreters.

>>>>

\section{Conclusion}
We have shown how JSExplain can be easily adapted to other programming language,
in this case OCaml. Most of the complexity of OCaml being its typing, writing
the interpreter was quite straightforward. The current implementation of our
interpreter is very simple and contains a lot of documentation. The
architecture of the code is also straightforward, which allows anyone to easily
extend the interpreter. The simple design of our interpreter makes it a perfect
candidate to base a specification of OCaml on. MLExplain also provides a
confortable environment to experiment with the semantics of OCaml. It is thus a
perfect playground for future evolution of the language.

As future work, we plan to extend the subset of OCaml supported by our
compiler, to be able to directly use the standard library when writing
interpreters.
